What is a Selection Coefficient?

### 2022-01-06 graphs_newt_snakes/What_is_sel_coef.Rmd
thinking about how to make bins

```{r, phenotype bins}

graph_file<-file

pmin = min(file$phenotype)
pmax = max(file$phenotype)
psd = sd(file$phenotype)
pmean = mean(file$phenotype)

bin(file$phenotype)
graph_file$

>>>>

```{r, phenotype bins}
library(OneR)
graph_file<-file
data = file$phenotype
pmin = min(file$phenotype)
pmax = max(file$phenotype)
psd = sd(file$phenotype)
pmean = mean(file$phenotype)

mybins = bin(file$phenotype, nbins = 3)
str(bin(data, nbins = 3, labels = c("small", "medium", "large")))
